TRITON: Globally Consistent Sim-to-Real Transfer

### 2022-06-04 CORL/example.tex
example.tex: Fixed image paths

% \usepackage{corl_2022} % Use this for the initial submission.
\usepackage[final]{corl_2022} % Uncomment for the camera-ready ``final'' version.
\usepackage{graphicx}
\usepackage{float}
\graphicspath{ {../images} }

@@

\begin{figure}[H]
	\begin{center}
		\includegraphics[width=200pt]{dataset_explanation.pdf}
	\end{center}
	\caption{
		Compatiable datasets have two sets of images: a set of UVL scenes and a set of photographs.
		TRITON is a sim-to-real image translation algorithm, taking in synthetic UVL scenes and aiming to create realistic fake photographs. 
		Being an unsupervised algorithm, there are no correspondences between synthetic and real images.
		In this dataset, three alphabet cubes are moved around the table. 
		The synthetic and real cameras have the same position and field of view.
		There are many more UVL scenes than photos, because synthetic scenes can be generated automatically whereas photos require real-world labor.
		}
	\label{fig:dataset_explanation}
\end{figure}

\begin{figure}[H]
	\begin{center}
		\includegraphics[width=270pt]{uvl_explanation.pdf}
	\end{center}
	\caption{
		This diagram shows the purpose of a UVL image.
		 A UVL scene is an image that has three channels: RGB.
		 R and G are used for U and V, and B is used for L.
		 L stands for Label, and determines which part of the synthetic image will get which texture.
		 The U and V coordinates correspond to positions on each texture,
		 	telling it how to project the textures onto the 3d objects represented in the UVL scene.
		The darkest shade of blue corresponds to the 1st texture, and the next darkest shade of blue corresponds to the 2nd texture etc.
		}
	\label{fig:uvl_explanation}
\end{figure}

@@

\begin{figure}[H]
	\begin{center}
		\includegraphics[width=400pt]{main_diagram_condensed.pdf}
	\end{center}
	\caption{
		This is the main diagram for the paper. $B$ is the batch size, and $L$ is the number of different labels (which is also the number of learnable textures).
		TODO: Come up with a tour of this diagram in this caption. Also maybe make it larger?
		TODO: Use variables instead of 3,4
		TODO: Make the text larger and easier to read
		TODO: Simplify the diagram?
	}
	\label{fig:main_diagram}
\end{figure}

\begin{figure}[H]
	\begin{center}
		\includegraphics[width=400pt]{unprojection_consistency_loss.pdf}
	\end{center}
	\caption{
		This is the unprojection consistency loss used in figure \ref{fig:main_diagram}.
		After calculating fake photos $\hat{p}_{1...B}$ from UVL scenes $\u_{1...R,1...L}$, 
		\pi
	}
	\label{fig:unprojection_consistency_loss}
\end{figure}

@@

\section{Citations}
\label{sec:citations}
\begin{figure}[H]
	\begin{center}
		\includegraphics[width=400pt]{frame_inconsistency_diagram.pdf}
	\end{center}

>>>>

% \usepackage{corl_2022} % Use this for the initial submission.
\usepackage[final]{corl_2022} % Uncomment for the camera-ready ``final'' version.
\usepackage{graphicx}
\usepackage{float}

@@

\begin{figure}[H]
	\begin{center}
		\includegraphics[width=200pt]{../images/dataset_explanation.pdf}
	\end{center}
	\caption{
		Compatiable datasets have two sets of images: a set of UVL scenes and a set of photographs.
		TRITON is a sim-to-real image translation algorithm, taking in synthetic UVL scenes and aiming to create realistic fake photographs. 
		Being an unsupervised algorithm, there are no correspondences between synthetic and real images.
		In this dataset, three alphabet cubes are moved around the table. 
		The synthetic and real cameras have the same position and field of view.
		There are many more UVL scenes than photos, because synthetic scenes can be generated automatically whereas photos require real-world labor.
		}
	\label{fig:dataset_explanation}
\end{figure}

\begin{figure}[H]
	\begin{center}
		\includegraphics[width=270pt]{../images/uvl_explanation.pdf}
	\end{center}
	\caption{
		This diagram shows the purpose of a UVL image.
		 A UVL scene is an image that has three channels: RGB.
		 R and G are used for U and V, and B is used for L.
		 L stands for Label, and determines which part of the synthetic image will get which texture.
		 The U and V coordinates correspond to positions on each texture,
		 	telling it how to project the textures onto the 3d objects represented in the UVL scene.
		The darkest shade of blue corresponds to the 1st texture, and the next darkest shade of blue corresponds to the 2nd texture etc.
		}
	\label{fig:uvl_explanation}
\end{figure}

@@

\begin{figure}[H]
	\begin{center}
		\includegraphics[width=400pt]{../images/main_diagram_condensed.pdf}
	\end{center}
	\caption{
		This is the main diagram for the paper. $B$ is the batch size, and $L$ is the number of different labels (which is also the number of learnable textures).
		TODO: Come up with a tour of this diagram in this caption. Also maybe make it larger?
		TODO: Use variables instead of 3,4
		TODO: Make the text larger and easier to read
		TODO: Simplify the diagram?
	}
	\label{fig:main_diagram}
\end{figure}

\begin{figure}[H]
	\begin{center}
		\includegraphics[width=400pt]{../images/unprojection_consistency_loss.pdf}
	\end{center}
	\caption{
		This is the unprojection consistency loss used in figure \ref{fig:main_diagram}.
		After calculating fake photos $\hat{p}_{1...B}$ from UVL scenes $\u_{1...R,1...L}$, 
	}
	\label{fig:unprojection_consistency_loss}
\end{figure}

@@

\section{Citations}
\label{sec:citations}
\begin{figure}[H]
	\begin{center}
		\includegraphics[width=400pt]{../images/frame_inconsistency_diagram.pdf}
	\end{center}
